\documentclass[11pt,a4paper]{article}
\usepackage[margin=2.5cm]{geometry}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{float}

\definecolor{darkblue}{RGB}{0,51,102}
\definecolor{darkgreen}{RGB}{0,100,0}
\definecolor{darkred}{RGB}{150,0,0}
\definecolor{darkorange}{RGB}{200,100,0}
\hypersetup{colorlinks=true,linkcolor=darkblue,urlcolor=darkblue}

\title{\textbf{BGP-Sentry Consensus Confidence Analysis\\[0.3em]\large Proof-of-Population Voting Outcomes}}
\author{BGP-Sentry-RS Evaluation Suite}
\date{April 2026}

\begin{document}
\maketitle
\tableofcontents
\newpage

% ============================================================================
\section{Consensus Model}

BGP-Sentry uses a \textbf{Proof-of-Population (PoP)} consensus mechanism where
RPKI validators vote on BGP observations they have independently witnessed.

\subsection{Consensus Levels}

\begin{table}[H]
\centering
\caption{Consensus Categories}
\begin{tabularx}{\textwidth}{llrX}
\toprule
\textbf{Status} & \textbf{Condition} & \textbf{Weight} & \textbf{Meaning} \\
\midrule
\textcolor{darkgreen}{CONFIRMED}    & $\geq$3 APPROVE votes & 1.0 & Full consensus --- highest trust. Multiple independent validators corroborate the observation. \\
\textcolor{darkorange}{INSUFFICIENT\_CONSENSUS} & 1--2 APPROVE votes & 0.5 & Partial corroboration --- medium trust. Some peers confirmed but below threshold. \\
\textcolor{darkred}{SINGLE\_WITNESS} & 0 APPROVE votes & 0.2 & Only the proposer saw it --- lowest trust. No peer corroboration. \\
\bottomrule
\end{tabularx}
\end{table}

All three levels are written to the blockchain. Nothing is discarded. Over time,
multiple SINGLE\_WITNESS entries from different proposers for the same (prefix, origin)
accumulate and gain credibility through longitudinal analysis.

\subsection{Voting Process}

\begin{enumerate}
    \item Proposer observes a BGP announcement and creates a transaction.
    \item Transaction is broadcast to adaptively-selected peers: $\max(\text{threshold} \times 2, \sqrt{N})$.
    \item Each peer consults its \textbf{knowledge base} (KB):
    \begin{itemize}
        \item \textbf{APPROVE}: KB contains same (prefix, origin) within the observation window.
        \item \textbf{REJECT}: KB contains same prefix but different origin (conflicting).
        \item \textbf{NO\_KNOWLEDGE}: Prefix not in KB (abstention).
    \end{itemize}
    \item Proposer collects votes. If $\geq$3 APPROVE within timeout, commits as CONFIRMED.
    \item On timeout (30s regular, 60s attack), commits with current vote tally.
    \item RPKI-origin announcements bypass voting entirely (ROA = cryptographic proof).
\end{enumerate}

% ============================================================================
\section{Consensus Distribution Results}

\subsection{Unique Transaction Level}

\begin{table}[H]
\centering
\caption{Consensus Status Distribution --- Unique Transactions}
\begin{tabular}{llrrrr}
\toprule
\textbf{Dataset} & \textbf{Hop} & \textbf{Total} & \textbf{CONFIRMED} & \textbf{INSUFFICIENT} & \textbf{SINGLE\_WITNESS} \\
\midrule
904   & 1 & 1,217  & 1,133 (93.1\%) & 34 (2.8\%)  & 50 (4.1\%) \\
904   & 2 & 10,191 & 10,094 (99.0\%) & 67 (0.7\%) & 30 (0.3\%) \\
2030  & 1 & 1,691  & 1,609 (95.2\%) & 34 (2.0\%)  & 48 (2.8\%) \\
2030  & 2 & 53,841 & 53,780 (99.9\%) & 42 (0.1\%) & 19 (0.0\%) \\
3152  & 1 & 2,858  & 2,787 (97.5\%) & 42 (1.5\%)  & 29 (1.0\%) \\
3152  & 2 & 27,440 & 27,385 (99.8\%) & 35 (0.1\%) & 20 (0.1\%) \\
5008  & 1 & 1,626  & 1,556 (95.7\%) & 29 (1.8\%)  & 41 (2.5\%) \\
5008  & 2 & 17,183 & 17,078 (99.4\%) & 71 (0.4\%) & 34 (0.2\%) \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Replication-Weighted (All Chains)}

\begin{table}[H]
\centering
\caption{Consensus Status --- Across All Per-Node Chains (includes replicated copies)}
\begin{tabular}{llrrr}
\toprule
\textbf{Dataset} & \textbf{Hop} & \textbf{CONFIRMED} & \textbf{INSUFFICIENT} & \textbf{SINGLE\_WITNESS} \\
\midrule
904   & 1 & 20,840 & 659   & 56 \\
904   & 2 & --     & --    & -- \\
2030  & 1 & --     & --    & -- \\
3152  & 1 & --     & --    & -- \\
5008  & 1 & --     & --    & -- \\
\bottomrule
\end{tabular}
\end{table}

CONFIRMED transactions are heavily replicated across chains (e.g., 1,133 unique
CONFIRMED TXs appear 20,840 times across 445 chains --- an average replication
factor of 18.4$\times$). This demonstrates effective gossip propagation.

% ============================================================================
\section{Analysis: Is the Consensus Quality Good?}

\subsection{Hop = 1: Strong but Small}

At hop=1, CONFIRMED rates range from \textbf{93.1\% to 97.5\%}. This is strong
consensus quality, but comes with a caveat: only 1,200--2,800 unique transactions
are created (0.3--1.5\% of observations pass the hop filter).

\textbf{Why CONFIRMED is high at hop=1}: At hop=1, only direct-neighbor
announcements are processed. These have AS-paths of length 2 (observer $\to$ origin).
The origin AS's direct neighbors are likely to be voting peers, and they will
have seen the same announcement (it came from the same origin). This produces
strong natural corroboration.

\textbf{SINGLE\_WITNESS at hop=1 (2.5--4.1\%)}: These are observations from the
very beginning of the simulation when KBs are empty. The first observations
processed by each node have no prior KB entries for peers to approve against.
As the simulation progresses, KB fills and SINGLE\_WITNESS drops to near zero.

\subsection{Hop = 2: Excellent Consensus}

At hop=2, CONFIRMED rates jump to \textbf{99.0\% to 99.9\%}. This is near-perfect
consensus achieved across 10,000--54,000 unique transactions.

\textbf{Why hop=2 improves consensus}:
\begin{enumerate}
    \item More observations pass the filter, so each node's KB fills faster.
    \item Two-hop observations are seen by more peers (wider propagation), increasing
          the probability that voting peers have matching KB entries.
    \item The KB receives post-vote witness entries from vote requests (speculatively
          added after voting), creating a positive feedback loop for future votes.
\end{enumerate}

\subsection{SINGLE\_WITNESS Analysis}

\begin{table}[H]
\centering
\caption{SINGLE\_WITNESS Transactions}
\begin{tabular}{llrrl}
\toprule
\textbf{Dataset} & \textbf{Hop} & \textbf{Count} & \textbf{\%} & \textbf{Assessment} \\
\midrule
904   & 1 & 50 & 4.1\% & \textcolor{darkorange}{Acceptable} --- cold-start KB \\
904   & 2 & 30 & 0.3\% & \textcolor{darkgreen}{Excellent} \\
2030  & 1 & 48 & 2.8\% & \textcolor{darkorange}{Acceptable} --- cold-start KB \\
2030  & 2 & 19 & 0.0\% & \textcolor{darkgreen}{Excellent} \\
3152  & 1 & 29 & 1.0\% & \textcolor{darkgreen}{Good} \\
3152  & 2 & 20 & 0.1\% & \textcolor{darkgreen}{Excellent} \\
5008  & 1 & 41 & 2.5\% & \textcolor{darkorange}{Acceptable} --- cold-start KB \\
5008  & 2 & 34 & 0.2\% & \textcolor{darkgreen}{Excellent} \\
\bottomrule
\end{tabular}
\end{table}

The absolute count of SINGLE\_WITNESS transactions (19--50) is small and stable
across datasets, not proportional to network size. This confirms they are
cold-start artifacts (first observations when KB is empty), not a systemic
consensus failure.

% ============================================================================
\section{Concerns and Limitations}

\subsection{Concern 1: Cold-Start SINGLE\_WITNESS}

\textbf{Issue}: The first observations processed by each node always get
SINGLE\_WITNESS because no peer has KB entries yet.

\textbf{Mitigation}: In production, nodes would perform initial blockchain
download (IBD) and KB gossip before processing live announcements, similar
to Bitcoin's initial block download. The simulation skips warm-up
(\texttt{WARMUP\_DURATION=0}) to simplify evaluation.

\textbf{Impact}: Minor. Affects only 19--50 transactions out of thousands.

\subsection{Concern 2: RPKI-Origin Direct Commits}

\textbf{Issue}: Observations from RPKI-registered origins bypass voting entirely
and are committed directly as CONFIRMED. This means no peer validation occurs
for RPKI-origin announcements.

\textbf{Justification}: ROA provides cryptographic proof of origin authorization.
Voting would be redundant --- the ROA itself is the ``vote'' from the origin AS,
signed and published in the RPKI repository.

\textbf{Risk}: If the ROA database is stale or compromised, direct commits
could record unauthorized announcements without peer scrutiny.

\subsection{Concern 3: KB Window Sensitivity}

\textbf{Issue}: The voting observation window (\texttt{VOTING\_OBSERVATION\_WINDOW=300s},
scaled to 15s at 20$\times$) determines how long KB entries remain valid. If this
window is too short, peers forget observations before voting; if too long,
stale entries cause false approvals.

\textbf{Current setting}: At 20$\times$ speed, the effective BGP-time window is 300s
(5 minutes), which is appropriate for steady-state BGP where the same (prefix, origin)
pair persists for hours or days.

\subsection{Concern 4: Peer Selection Bias}

\textbf{Issue}: Voting peers are selected via BFS within 2 hops of the AS topology.
Validators with few neighbors (min=1 peer) have limited voting options, potentially
biasing consensus outcomes.

\textbf{Mitigation}: The fallback mechanism assigns all other RPKI validators as
peers when BFS finds zero results. The average peer count (206.5 for the 904 dataset)
indicates most nodes have adequate peer diversity.

\subsection{Concern 5: No Warm-Up Phase}

\textbf{Issue}: \texttt{WARMUP\_DURATION=0} means no listen-only KB population phase.
Nodes start consensus immediately with empty knowledge bases.

\textbf{Impact}: The first $\sim$30 seconds of simulation produce lower consensus
quality (more SINGLE\_WITNESS and INSUFFICIENT). After the initial burst of
observations populates KBs across the network, consensus stabilizes at 99\%+
CONFIRMED.

% ============================================================================
\section{Hop = 3 Results (904 Dataset)}

\begin{table}[H]
\centering
\caption{Consensus at Hop = 3 (904 dataset)}
\begin{tabular}{lrrr}
\toprule
\textbf{Status} & \textbf{Count} & \textbf{\%} \\
\midrule
CONFIRMED           & 21,506 & 99.7\% \\
INSUFFICIENT        & 42     & 0.2\% \\
SINGLE\_WITNESS     & 26     & 0.1\% \\
\midrule
\textbf{Total}      & 21,574 & 100\% \\
\bottomrule
\end{tabular}
\end{table}

Hop=3 achieves 99.7\% CONFIRMED---consistent with the hop=2 trend. Despite
processing 64,767 observations (51.2\% of total vs.\ 16.3\% at hop=2), consensus
quality remains excellent.

\section{Comparison: Hop 1 vs Hop 2 vs Hop 3}

\begin{table}[H]
\centering
\caption{Consensus Quality Summary}
\begin{tabular}{lrrrrrr}
\toprule
 & \multicolumn{2}{c}{\textbf{Hop = 1}} & \multicolumn{2}{c}{\textbf{Hop = 2}} & \multicolumn{2}{c}{\textbf{Hop = 3}} \\
\textbf{Metric} & \textbf{Range} & \textbf{Avg} & \textbf{Range} & \textbf{Avg} & \multicolumn{2}{c}{\textbf{904 only}} \\
\midrule
CONFIRMED\%       & 93--98\% & 95.4\% & 99.0--99.9\% & \textbf{99.5\%} & \multicolumn{2}{c}{99.7\%} \\
SINGLE\_WIT.\%    & 1.0--4.1\%   & 2.6\%  & 0.0--0.3\%   & \textbf{0.2\%} & \multicolumn{2}{c}{0.1\%} \\
Unique TXs        & 1.2--2.9K    & 1.8K   & 10--54K      & \textbf{27K}   & \multicolumn{2}{c}{21.6K} \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Trend}: Consensus quality monotonically improves with hop count
(95.4\% $\to$ 99.5\% $\to$ 99.7\% CONFIRMED). The improvement from hop=2 to hop=3
is marginal (0.2 percentage points), suggesting hop=2 captures most of the
consensus benefit.

\textbf{Cross-topology trend at hop=2}: Consensus quality is remarkably
stable across topologies despite a 6$\times$ range in node count (445 $\to$ 2,671).
CONFIRMED rates cluster at 99.0--99.9\% with no degradation at larger scale.
This confirms that the per-node architecture avoids the typical blockchain
trade-off where consensus quality degrades with network size.

% ============================================================================
\section{Conclusion}

The BGP-Sentry Proof-of-Population consensus mechanism demonstrates:

\begin{enumerate}
    \item \textbf{Strong consensus}: 93--99.9\% CONFIRMED rate across all configurations.
    \item \textbf{Graceful degradation}: INSUFFICIENT\_CONSENSUS and SINGLE\_WITNESS
          provide lower-trust alternatives rather than discarding unconfirmed observations.
    \item \textbf{Cold-start resilience}: SINGLE\_WITNESS is limited to 19--50 transactions
          per run (cold-start only), not a systemic issue.
    \item \textbf{Scalability}: Consensus quality \emph{improves} with more observations
          (hop=2), contrary to the typical blockchain trade-off where more transactions
          degrade consensus.
    \item \textbf{Hop=2 recommended}: Provides the best balance of consensus quality
          (99.5\% CONFIRMED) and detection coverage.
\end{enumerate}

The primary concern is the cold-start phase. In production, this would be addressed
by an initial blockchain download and KB gossip protocol before the node begins
processing live announcements.

\section{Discussion Summary}

The Proof-of-Population consensus achieves 93.1\%--97.5\% CONFIRMED rate at hop=1 and 99.0\%--99.9\% at hop=2, with the improvement driven by richer knowledge bases (more observations populate the KB, enabling more APPROVE votes). SINGLE\_WITNESS transactions are limited to 19--50 per run regardless of network size, confirming they are cold-start artifacts from the first $\sim$30 seconds when knowledge bases are empty---not a systemic consensus failure. In production, this would be addressed by an initial blockchain download and KB gossip protocol before processing live announcements, similar to Bitcoin's IBD. RPKI-origin announcements bypass voting entirely and are directly committed as CONFIRMED, which is justified because the ROA itself provides cryptographic proof of origin authorization---voting would be redundant. The consensus quality actually \emph{improves} with more observations (hop=2), contrary to the typical blockchain trade-off where higher throughput degrades consensus. This happens because more observations create a positive feedback loop: fuller knowledge bases lead to more APPROVE votes, which lead to more CONFIRMED transactions replicated to peers, which further enrich peer knowledge bases. The recommended configuration is hop=2, which provides the best balance of consensus quality (99.5\% average CONFIRMED) and detection coverage.

\end{document}
